CF Registry Analysis

### 2023-05-18 Christine Chan/CF Registry/cf_registry_analysis.qmd
CFRD registry logistic models mostly done

```{r}
# Import and clean data
annual <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",
                   na.strings = c("", "N/A")
)
annual = annual %>% filter(cfrd_status_annual != 4,cfrd_status_annual != 5)
annual$cfrd_status_annual = factor(annual$cfrd_status_annual,levels = 1:3,
                                   labels = c("CFRD-","CFRD-","CFRD+"))

demogs = read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_DemogCFDiag_Del1.csv")
demogs = demogs %>% select(eDWID,Gender,MutClass)

encounter <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_encountersMerged_Del1.csv",

@@

mods = encounter %>% group_by(eDWID,reviewyear) %>%
  summarise(across(c(Vx770,Vx809comb),~max(.x,na.rm = T)),.groups = "drop")
annual = left_join(annual,mods)

@@

           A_corticosteroids1,cfrd_status_annual)

@@

@@

  base_mod = as.formula("cfrd_status_annual~Gender+Age_YrEnd+A_IsOnEnzymes+MutClass+
                   A_FEV1_pct_predicted+NumPulmExacerbation+A_feeding2")

@@

  # Add bugs
  # P. aeruginosa
  # Aspergillus
  # ABPA
  # Mycobacterium
  adult_mod5 = glm(update(adult_mod,.~.+A_pulmonarycomplications1),data = df,family = "binomial")
  peds_mod5 = glm(update(peds_mod,.~.+A_pulmonarycomplications1),data = df,family = "binomial")

@@

@@

@@

@@

>>>>

```{r}
# Import and clean data
annual <- read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_Annualized_Del1.csv",

@@

annual = annual %>% filter(cfrd_status_annual != 4,cfrd_status_annual != 5)
annual$cfrd_status_annual = factor(annual$cfrd_status_annual,levels = 1:3,
                                   labels = c("CFRD-","CFRD-","CFRD+"))
demogs = read.csv("/Users/timvigers/Documents/Work/Christine Chan/CF registry data/CFF19_DemogCFDiag_Del1.csv")
demogs = demogs %>% select(eDWID,Gender,MutClass)

@@

           A_corticosteroids1,cfrd_status_annual,A_Vx770,A_VX809comb)

@@

  df$A_Vx770 = factor(df$A_Vx770,levels = 0:1,labels = c("No","Yes"))
  df$A_VX809comb = factor(df$A_VX809comb,levels = 0:1,labels = c("No","Yes"))
  # Remove all empty columns
  df = df[,-which(colSums(is.na(df))==nrow(df))]
  # Bugs
  bugs = c("A_pseudomonasaeruginosa","A_fungalyeast1",
           "A_pulmonarycomplications1","A_mycocultureresults1")

@@

  vars = colnames(df)[which(!colnames(df) %in% 
                              c(bugs,"cfrd_status_annual","eDWID","A_bmivalue",
                                "A_bmipercentile","A_height","A_heightpercentile"))]
  base_mod = as.formula(paste0("cfrd_status_annual~",paste0(vars,collapse = "+")))

@@

@@

  if ("A_pseudomonasaeruginosa" %in% colnames(df)){

@@

  if("A_fungalyeast1" %in% colnames(df)){

@@

  if("A_pulmonarycomplications1" %in% colnames(df)){

@@

  if("A_mycocultureresults1" %in% colnames(df)){
    adult_mod5 = glm(update(adult_mod,.~.+A_mycocultureresults1),data = df,family = "binomial")
    peds_mod5 = glm(update(peds_mod,.~.+A_mycocultureresults1),data = df,family = "binomial")
